### 2023-05-02 Documentation/UFMG/PFCII/Abstract/Abstract.tex
documentation

    Electrohydrodynamic Atomization (EHDA), also called electrospray, is a liquid atomization technique that
    produces micro- and nanometric charged droplets within a narrow size distribution by using high electric fields (kV/cm).
    According to Cloupeau and Prunet-Foch\cite{prunet} (1994), electrosprays can generate droplets in different ways, which the authors
    named "electrospray modes". These modes may be adjusted by varying the strength of the electric field and flow rate,
    but also depend on liquid properties and system geometry. In their work, the authors proposed four possible EHDA
    modes: dripping, intermittent, cone-jet and multi-jet, which are generally distinguished visually. Verdoold et al.\cite{Sjaaks} (2014)
    recently suggested a classification approach based on the behavior of the electric current of the electrospray process.

    This project develops a closed-loop control method for EHDA devices that uses real-time, electric current-based (hence
    non-visual) spray mode classification.
    The proposed electrospray system is entirely automatic, where all the peripherals, such as HV power supply and syringe
    pump, are controlled by a computer which executes their routines.
    The system classifies spray mode dynamics using real-time current data and changes EHDA operating parameters such
    as liquid flowrate and applied voltage to achieve and maintain the chosen spray mode. The electrospray modes are
    validated in real time by using a high-speed camera.
    As compared to conventional manual approaches, the implemented control algorithm achieves higher
    accuracy and lower transient time. Therefore, a completely autonomous EHDA system opens the door to potential
    industrial applications. In addition, the use of the electric current signal will be useful to further study electrospray
    processes, leading to better control on droplet generation (frequency, size and charge). The incorporation of Machine
    Learning to improve mode categorization will be a future development.

\clearpage
\thispagestyle{empty}
\cleardoublepage

>>>>

    Electrohydrodynamic Atomization (EHDA), also called electrospray, is a liquid atomization technique that
    produces micro and nanometric charged droplets within a narrow size distribution by using high electric fields (kV/cm).
    According to Cloupeau and Prunet-Foch\cite{prunet} (1994), electrosprays can generate droplets in different ways, which the authors
    named "electrospray modes". These modes may be adjusted by varying the strength of the electric field and flow rate,
    but also depend on liquid properties and system geometry. In their work, the authors proposed four possible EHDA
    modes: dripping, intermittent, cone-jet and multi-jet, which are generally distinguished visually.

    This project develops a closed-loop control method for EHDA devices that uses real-time, electric current-based (hence
    non-visual) spray mode classification.
    The proposed electrospray system is entirely automatic, where all the peripherals, such as HV power supply and syringe
    pump, are controlled by a computer which executes their routines.
    The system classifies spray mode dynamics using real-time current data and changes EHDA operating parameters such
    as liquid flow rate and applied voltage to achieve and maintain the chosen spray mode. The electrospray modes are
    validated in real time by using a high-speed camera.
    As compared to conventional manual approaches, the control algorithm promises higher
    accuracy and lower transient time. Therefore, a completely autonomous EHDA system opens the door to potential
    industrial applications. In addition, the use of the electric current signal can be useful to further research in electrospray
    processes, leading to better control on droplet generation (frequency, size and charge).

### 2023-05-02 Documentation/UFMG/PFCII/Introduction/Introduction.tex
documentation

The spraying process imposes noise and random sequences on the measured signal making it sorting is not a trivial task.
Industrial applications require automated stabilization of a spray mode. 
This can be achieved by a closed system loop control system. 
Automated spray mode sorting is a crucial part of a control system, as well as the development of an appropriate control algorithm.

@@

This project aims to give continuity to the previous student work\cite{Monica}, 
Mônica, who focused in detecting undesired discharges (sparks) in the system accusing high electric potential. 
For that, she developed a python software routine to connect most of the peripherals and analyzed the current data.
Her work corroborates the validation of this project motivating its development and optimization.

Above is shown the main goals listed:

\begin{enumerate}[]
\item Multipurpose applications for both scientific and industrial approaches.
\item Fully automated and intuitive system for EHDA.
\item Real Time non-visual classification of spraying modes.
\item Control and stabilization on a desired dynamic. 
\item System portability and versatility.
\end{enumerate}

@@

>>>>

The spraying process imposes noise and random sequences on the measured signal making it sorting is not a trivial task.
Industrial applications require automated stabilization of a spray mode. 
This can be achieved by a closed system loop control system. 
An automated spray mode classification is a crucial part of the control system to work, as well as the development of an appropriate control algorithm.

@@

This project aims to give continuity to the previous student work\cite{Monica}, 
Mônica, who focused in detecting undesired discharges (sparks) in the system accusing high electric potential. 
For that, she developed a python software routine to connect most of the peripherals and analyzed the current data.
Her work corroborates the validation of this project motivating its continuation on development and optimization.

Bellow are shown the main goals listed:

\begin{enumerate}[]
\item Multipurpose applications for both scientific and industrial approaches.
\item Fully automated and intuitive system for EHDA.
\item Real time non-visual classification of spraying modes.
\item Control and stabilization on a desired dynamic. 
\item System portability and versatility.
\end{enumerate}

@@

This document is divided in 6 chapters. 
This chapter \ref{chap:intro} shows an introduction about EHDA and what inspired the project. 
Chapter \ref{chap:lit_review} have a more deep explanation about the literature concepts and knowledge used in this project. 
Chapter \ref{chap:system_description} will describe all the system implemented to make this project work with the instruments and models used to apply our methodology.
Chapter \ref{chap:Methodology} we present the methodology applied in our experiments in order to validate our system.
Chapter \ref{chap:Results} presents our results and discussions comparing the knowledge acquired in literature review.
Finally, chapter \ref{chap:conclusion} will conclude our document with discussions about what goals were achieved and what can be optimized.

### 2023-05-02 Documentation/UFMG/PFCII/LiteratureReview/LiteratureReview.tex
documentation

Therefore, researches were made about the classification of the spraying mode measuring the current flowing through the nozzle to plate\cite{Sjaaks}\cite{Chen_Pui}. 
Evaluating the current data can give us valuable information about the spraying behavior.
Figure \ref{fig:microdripping_current_pic} illustrate a sample of current measured in our system during a dripping of a charged liquid. 
We can visually identify the signal of two droplets generated in this time frame.

>>>>

Therefore, many researches were made about the classification of the spraying mode measuring the current flowing through the nozzle to plate\cite{Sjaaks}\cite{Chen_Pui}. 
Evaluating the current data can give us valuable information about the spraying behavior.
Figure \ref{fig:microdripping_current_pic} illustrate a sample of current measured in our system during a dripping of a charged liquid. 
We can visually identify the signal of two droplets generated in this time frame.
